---
title: "Statistical Series"
#author: "Telmo Brugnara"
#date: "December 20, 2016"
output: 
  html_document: 
    keep_md: yes
    #self_contained: no
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
library(ribge)
#library(knitr)
options(knitr.table.format = 'markdown')
```

Table with all series from IBGE's [Séries Estatísticas & Séries Históricas](http://seriesestatisticas.ibge.gov.br/).

After loading `ribge` package, you can find the same data in the `seriesEstatisticas`
*data_frame*. You may load a given series with the following code:

```{r example, eval=FALSE}
df <- series_estatisticas_carrega(codigo + "_" + nivel_geo + "_" + "ABS"|"PERC")
```

where `codigo` is the dataset identifier and `nivel_geo` the geographical level and
can be one of:

* **BR** - brasil
* **UF** - unidades-federativas
* **GR** - grandes-regioes
* **RM** - regioes-metropolitanas
* **CAP** - capitais
* **MUN** - municipios

Both `codigo` and `nivel_geo` can be found in the `seriesEstatisticas`
*data_frame* (shown bellow).

You also need to add `ABS` (absolute) or `PERC` (percentage) to the functions's argument
depending on its datatype.

Other parameters for `series_estatisticas_carrega`:

* **dir** - directory to save temporary data (defaults to current dir)
* **xtraurl** - extra parameters to send in the HTTP request (`localidade=Todas` may be useful for some datasets)
* **transpose** - transpose the dataset (years on the rows)

Some examples:

* `series_estatisticas_carrega("FDT221_BR_PERC")` - Employment-to-population ratio, 1992-2007 (BR, percentage)
* `series_estatisticas_carrega("FDT800_BR_ABS")` - Average income from wages, 1981-2007 (BR, absolute)

The Table
---------

```{r series, echo=FALSE}
#see http://kbroman.org/knitr_knutshell/pages/figs_tables.html
s <- seriesEstatisticas
s$descricao <- gsub("[\r\n]+", " ", s$descricao)
knitr::kable(s, digits=2)
```

